Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-10-27 paper/main.tex
Added supercop description, with sources

\begin{acronym}
\acro{AES}{Advanced Encryption Standard}
\acro{FEC}{Forward Error Correction}
\acro{LAFS}{Least-Authority Filesystem}
\acro{NIST}{National Institute of Standards and Technology}
\acro{RAM}{Random Access Memory}
\acro{SHA}{Secure Hash Algorithm}
\end{acronym}

@@

\subsection{SuperCop}
Supercop is a toolkit developed by VAMPIRE lab for measuring performance of
cryptographic software, among them the SHA-3 candidates. While security is a
primary goal of a hash function, performance can not be neglected if the hash
function should be taken into use. The difference between the implementations
in the official submissions and in supercop is first that the supercop
implementation are continiously updated and that there are more specific
hardwareimplementations available in supercop.

Results by the supercop are published at (URL).

Paralellizing

>>>>

\begin{acronym}
\acro{AES}{Advanced Encryption Standard}
\acro{FEC}{Forward Error Correction}
\acro{LAFS}{Least-Authority Filesystem}
\acro{NIST}{National Institute of Standards and Technology}
\acro{RAM}{Random Access Memory}
\acro{SHA}{Secure Hash Algorithm}
\acro{SSE2}{Streaming SIMD Extensions 2}
\acro{SSSE3}{Supplemental Streaming SIMD Extensions 3}
\acro{SUPERCOP}{System for Unified Performance Evaluation Related to
Cryptographic Operations and Primitives}
\end{acronym}

@@

\subsection{\ac{SUPERCOP}}
% TODO: Sjekk hvordan det er med sitering her
\ac{SUPERCOP} is a toolkit developed by VAMPIRE lab for measuring performance
of cryptographic software\cite{s_supercop}. In relation to hash functions
\ac{SUPERCOP} measures the following:

\begin{itemize}
    \item Time to hash a very short packet of data
    \item Time to hash a typical-size Internet packet
    \item Time to hash a long message
    \item Length of the hash output
\end{itemize}

The round 2 \ac{SHA}-3 candidates are all included in the toolkit, with a
number of different optimalizations for each candidate. Optimalizations range
from 32-/64-bit optimalizations, the use of extended instruction sets such as
\ac{SSE2} and \ac{SSSE3}, optimalizations for different number of cores and
others. Also the toolkit will try different compiler-optimalizations to get the
best results possible for each function.
% Skal jeg sitere kildekode her?

The benchmarking results for the \ac{SUPERCOP} toolkit of \ac{SHA}-3 candidates
and \ac{SHA}-2 functions on a number of different plattforms and architectures 
are available at
\footnote{\url{http://bench.cr.yp.to/results-sha3.html}}
